Textbook Knowledge on Hospital Information Management as Linked Data

### 2020-01-10 paper.tex
Update template to version from 2019/05/06

\section{Data Model}\label{sec:architecture}
\citet{domaene} contains an initial structure of the meta model.
\todo{Describe the meta model here}
The \textbf{Semantic Network of Information Management in Hospitals} (SNIK\footnote{Hospital means \enquote{Krankenhaus} in German.}) is a modular OWL 2 DL ontology.
The \enquote{meta model} defines three basic disjunctive classes and their possible relations: Roles (who), Function (does what) and Entity Types (and which information is therefore needed).
A set of modular subontologies define subclasses of those three classes and their relations as described by a certain knowledge source about information management in hospitals:
%from different sources:% three textbooks, an interview and a standard.

>>>>

\section{Data Model}\label{sec:architecture}
\citet{domaene} contains an initial structure of the meta model.
The \enquote{meta model} defines three basic disjunctive classes and their possible relations: Roles (who), Function (does what) and Entity Types (and which information is therefore needed).
A set of modular subontologies define subclasses of those three classes and their relations as described by a certain knowledge source about information management in hospitals:
The \textbf{Semantic Network of Information Management in Hospitals} (SNIK\footnote{Hospital means \enquote{Krankenhaus} in German.}) is a modular OWL 2 DL ontology.
%from different sources:% three textbooks, an interview and a standard.
